---
title: "Darren J. Yeo's Vita"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false # set it to true for a self-contained HTML page but it'll take longer to render
    css: [djyeo-cv.css]
    number_sections: false
links-to-footnotes: false
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

#### cv entries #####
cv_entries <- readxl::read_xlsx(here::here("data", "cv_entries.xlsx"))

#### publications #####
pubs <- readxl::read_xlsx(here::here("data", "pubs.xlsx")) %>% 
  arrange(order) %>% 
  select(-order)

#pubs <- map_df(pubs, ~gsub("\\.$", "", .x)) # this line removes any full-stop in all fields (not ideal for author list)

courses <- readxl::read_xlsx(here::here("data", "courses.xlsx"))
```

```{r GS}
My_GS <- scholar::get_profile("DZUvMiwAAAAJ&hl") # replace content with your Google Scholar profile ID
```

```{r}
# PDF <- FALSE # Set to TRUE when rendering to PDF via pagedown::chrome_print()
# if(PDF) {
#   header <- '
#   View online
#   <a href="" class="icon-block">
#       <i class="fas fafooter fa-globe"></i>
#   </a>
#   '
# } else {
#   header <- '
#   Download PDF
#   <a href="" class="icon-block">
#       <i class="fas fafooter fa-download"></i>
#   </a>
#   '
# }
```


<!-- <div class = "download"> -->
<!-- ```{r results = "asis"} -->
<!-- cat(header) -->
<!-- ``` -->

</div>

<div class = "footer",>
  <a href="mailto:darren.j.yeo@vanderbilt.edu" class="icon-block">
      <i class="fas fafooter fa-envelope"> | </i>
  </a>
  
  <!-- <a href="https://jiansh.wix.com/darrenyeo" class="icon-block"> -->
  <!--     <i class="fas fafooter fa-globe"> | </i> -->
  <!-- </a> -->

  <a href="https://orcid.org/0000-0003-1207-259X" class="icon-block">
      <i class="fab fafooter fa-orcid"> | </i>
  </a>

  <a href="https://www.researchgate.net/profile/Darren_Yeo2" class="icon-block">
      <i class="fab fafooter fa-researchgate"> | </i>
  </a>
  
  <a href="https://github.com/darrenjyeo" class="icon-block">
      <i class="fab fafooter fa-github"> | </i>
  </a>
  
  <a href="https://twitter.com/darrenjyeo" class="icon-block">
      <i class="fab fafooter fa-twitter"> | </i>
  </a>
  
  <a href="https://www.linkedin.com/in/darrenjyeo" class="icon-block">
      <i class="fab fafooter fa-linkedin-in"> </i>
  </a>
  
</div>


<div id = "block_container">

<div class = "first", id="bloc1">Darren J.</div>  
<div class = "last", id="bloc2">Yeo</div>

</div>

<div id = "position", class = "position">
Ph.D. Candidate | Neuroscience
</div>

<div id = "sub", class = "sub">

</div>

<div class="grid-container">

```{r summary, child = here::here("content", "summary.Rmd")}
```

```{r contact-info, child = here::here("content", "contact-info.Rmd")}
```

</div>

## Education {.education .nohead}

```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = ifelse(is.na(year_begin), what, paste0(what, ", ", "<span style= 'font-weight: 500'>", where, "</span>")),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
         what = ifelse(!is.na(url), 
                       paste0("[", what, "](", url, ")"), 
                       what)
         ) %>% 
  mutate(year = str_c(year_begin, " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable()
```

## Professional {.history .nohead}

```{r}
cv_entries %>% 
  filter(type == 'history') %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where, ". ", ifelse(is.na(additional_info), "", str_c(additional_info, "."))),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable()
```

<!-- <br class="pageBreak"/> -->

# Scholarship

<div class = "inote">
Icons link to additional content  
</div>

***Google Scholar*** metrics as of *`r Sys.Date()`*:
**Total citations**: `r My_GS$total_cites`
**h-index**: `r My_GS$h_index`
**i10-index**: `r My_GS$i10_index`

## Peer-Reviewed Publications

```{r}
make_cite <- function(authors,	year,	title = NULL,	journal = NULL,	volume = NULL,	
                      issue = NULL,	pages = NULL,	doi = NULL,	url = NULL,
                      book = NULL, place_published = NULL, conference = NULL,
                      poster = NULL, conf_loc = NULL, annual_meeting = NULL, cancelled = NULL,
                      ...) {
  
  if(!is.null(journal)) {
    journal <- paste0("*", journal, "*,")
  }
  
  if(!is.null(volume)) {
    volume <- paste0("*", volume, "*,")
  }
  
  if(!is.null(issue)) {
    volume <- paste0(gsub(",", "", volume), "(", issue, "),")
  }
  if(!is.null(doi) & !is.null(url)) {
    doi <- paste0("[doi: ", doi, "](", url, ")")
  }
  if(!is.null(pages)) {
    if(!is.null(book)) {
      pages <- paste0("(pp. ", pages, ").")
    }
    else {
     pages <- paste0(pages,".") 
    }
  }
  if(!is.null(book)) {
    book <- paste0("*", book, "*")
  }
  if(!is.null(place_published)) {
    place_published <- paste0(place_published, ".")
  }
  if(!is.null(conference)) {
    title <- paste0("*", title, "*")
    if(is.null(poster)) {
      if(annual_meeting) {
        conference <- paste0("Presentation at the annual ", conference, ".")
      }
      else {
        conference <- paste0("Presentation at the ", conference, ".")
      }
    }
    else if(poster) {
      if(cancelled) {
        if(annual_meeting) {
          conference <- paste0("Poster selected to be presented at the cancelled annual meeting of the ", 
                            conference,
                            ", ", 
                            conf_loc,
                            ".") 
          }
        else {
          conference <- paste0("Poster selected to be presented at the ", 
                             conference, 
                             ", ", 
                             conf_loc, 
                             ".") 
        }
      }
      else {
        if(annual_meeting) {
          conference <- paste0("Poster presented at the annual meeting of the ", 
                            conference,
                            ", ", 
                            conf_loc,
                            ".") 
          }
        else {
          conference <- paste0("Poster presented at the ", 
                             conference, 
                             ", ", 
                             conf_loc, 
                             ".") 
        }
      }
    }
    else {
      if(cancelled) {
        if(annual_meeting) {
          conference <- paste0("Talk selected to be presented at the cancelled annual meeting of the ", 
                            conference, 
                            ", ", 
                            conf_loc,
                            ".")
          }
        else {
        conference <- paste0("Talk selected to be presented at the cancelled ", 
                             conference, 
                             ",", 
                             conf_loc,
                            ".")
        }
      }
      else {
        if(annual_meeting) {
          conference <- paste0("Talk presented at the annual meeting of the ", 
                            conference, 
                            ", ", 
                            conf_loc,
                            ".")
          }
        else {
          conference <- paste0("Talk presented at the ", 
                             conference, 
                             ",", 
                             conf_loc,
                            ".")
        }
      }
    }
  }
  
  authors <- gsub(
    "Yeo, D. J.\\.?",
    "<span style= 'font-weight: 500'>Yeo, D. J.</span>", 
    authors)
   
  paste(authors, 
        paste0("(", year, ")."), 
        ifelse(is.na(title), "", paste0(title, ".")),
        conference,
        journal, 
        volume,
        ifelse(is.na(book), "", paste0(book, ".")),
        pages, 
        doi,
        place_published)
}

prpas <- pubs %>% 
  filter(type == "prpa") %>% 
  select(-type) 

each_cite <- split(prpas, seq_len(nrow(prpas)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_doc <- ifelse(
  !is.na(prpas$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         prpas$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(prpas$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         prpas$git_repo, 
         ")"
         ),
  ""
  )

fa_osf <- ifelse(
  !is.na(prpas$osf_repo), 
  paste0('[<i class="fas falink2 fa-file"></i>](', 
         prpas$osf_repo, 
         ")"
         ),
  ""
  )

fa_media <- ifelse(
  !is.na(prpas$media), 
  paste0('[<i class="fas falink2 fa-newspaper"></i>](', 
         prpas$media, 
         ")"
         ),
  ""
  )

pubs_tbl <- tibble(year = prpas$year,
                  count = paste0(seq(length(formatted_cites), 1), "."),
                  cites = paste(unlist(formatted_cites), fa_doc, fa_git, fa_osf, fa_media)) 

pubs_tbl <- pubs_tbl %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year) %>%
  mutate(year = gsub("in press", "2020", year))
```

<div class = "hangingindent prpa nohead">

```{r} 
kable(pubs_tbl[seq(1, 9), ])
```

</div>

<br class="pageBreak"/>
<div class = "hangingindent prpa nohead">

```{r}
kable(pubs_tbl[seq(10, nrow(pubs_tbl)), ])
```

</div>

## Manuscripts Under Review for Publication {.submitted .nohead}

<div class = "hangingindent">

```{r }
submitted <- pubs %>% 
  filter(type == "in-review") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(submitted$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         submitted$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(submitted$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         submitted$git_repo, 
         ")"
         ),
  ""
  )

fa_osf <- ifelse(
  !is.na(submitted$osf_repo), 
  paste0('[<i class="fas falink2 fa-file"></i>](', 
         submitted$osf_repo, 
         ")"
         ),
  ""
  )

fa_media <- ifelse(
  !is.na(submitted$media), 
  paste0('[<i class="fas falink2 fa-newspaper"></i>](', 
         submitted$media, 
         ")"
         ),
  ""
  )

each_cite <- split(submitted, seq_len(nrow(submitted)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

if(length(formatted_cites) > 0) {
 submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                         cites = paste(unlist(formatted_cites), fa_doc, fa_git, fa_osf, fa_media)) 
kable(submitted_tbl)
}
```

</div>

## Books/Book Chapters

<div class = "hangingindent prpa nohead">

```{r}
chapters <- pubs %>% 
  filter(type == "book-chapter") %>% 
  select(-type)

each_cite <- split(chapters, seq_len(nrow(chapters)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

chapters_tbl <- tibble(year = chapters$year,
                       count = paste0(seq(length(formatted_cites), 1), "."),
                        cites = unlist(formatted_cites))

chapters_tbl <- chapters_tbl %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>%
  select(-count_within_year) %>%
  mutate(year = gsub("forthcoming", "2021", year))

kable(chapters_tbl[seq(1, nrow(chapters_tbl)), ])
```

</div>

## National & International Conference Presentations {.prpa .nohead}

<div class = "hangingindent">

```{r}
confs <- pubs %>% 
  filter(type == "conference") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(confs$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         confs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(confs$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         confs$git_repo, 
         ")"
         ),
  ""
  )

fa_osf <- ifelse(
  !is.na(confs$osf_repo), 
  paste0('[<i class="fas falink2 fa-file"></i>](', 
         confs$osf_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(confs$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         confs$slides_link, 
         ")"
         ),
  ""
  )


each_cite <- split(confs, seq_len(nrow(confs)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

conf_tbl <- tibble(year = confs$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), fa_doc, fa_pres, fa_git, fa_osf)
                   )
  
conf_tbl <- conf_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

kable(conf_tbl[seq(1, 1), ])
```

</div>

<br class="pageBreak">

<div class = "hangingindent">

```{r}
kable(conf_tbl[seq(2, 11), ])
```

</div>

<br class="pageBreak">

<div class = "hangingindent">

```{r}
kable(conf_tbl[seq(12, nrow(conf_tbl)), ])
```

</div>
## Regional Conference Presentations {.prpa .nohead}

<div class = "hangingindent">

```{r}
regional <- pubs %>% 
  filter(type == "regional") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(regional$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         regional$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(regional$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         regional$git_repo, 
         ")"
         ),
  ""
  )

fa_osf <- ifelse(
  !is.na(regional$osf_repo), 
  paste0('[<i class="fas falink2 fa-file"></i>](', 
         regional$osf_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(regional$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         regional$slides_link, 
         ")"
         ),
  ""
  )


each_cite <- split(regional, seq_len(nrow(regional)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

regional_tbl <- tibble(year = regional$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_doc,fa_pres,fa_git, fa_osf)
                   )
  
regional_tbl <- regional_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

kable(regional_tbl[seq(1, 2), ])
```

</div>

<br class="pageBreak">

<div class = "hangingindent">

```{r}
kable(regional_tbl[seq(3, nrow(regional_tbl)), ])
```

</div>

<!-- <br class="pageBreak"> -->

# Grants

<div class = "inote">
Icons link to additional content
</div>

```{r}
grants <- readxl::read_xlsx(here::here("data", "grants.xlsx"))

make_grant_cite <- function(title, funding_agency, award_num, role, pi,
  date_start, date_end, budget, fte_low_range, fte_high_range, contract,
  link, in_review = FALSE, ...) {

  if(in_review) {
    budg <- paste0(". Proposed budget: $",
                   prettyNum(budget, big.mark = ",")
                   )
  } else {
    budg <- paste0(". Total budget: $",
                    prettyNum(budget, big.mark = ",")
                    )
  }
  funder <- paste0("*", funding_agency, "* ")
  if(!is.na(award_num)) {
    funder <- paste0(funder, " (Award #", award_num, "). ")
  }
  if(fte_low_range != fte_high_range) {
    fte <- paste0("FTE: ",
                  format(fte_low_range, nsmall = 2),
                  " to ",
                  format(fte_high_range, nsmall = 2),
                  " across project years.")
  }
  else {
    fte <- paste0("FTE: ", format(fte_low_range, nsmall = 2), ".")
  }

  cite <- paste0(paste0(title, ". "),
                 paste(month(date_start, label = TRUE, abbr = FALSE),
                       year(date_start),
                       "to",
                       month(date_end, label = TRUE, abbr = FALSE),
                       year(date_end)),
                 budg,
                 paste0(". ",
                        "<span style= 'font-weight: 500'> Role: </span>",
                        role,
                        ". ")
                )
  cite <- ifelse(!is.na(pi),
                 paste0(cite, " PI: ", pi, "."),
                 cite)
  icon <- ifelse(!is.na(link),
                 paste('<a href=',
                       link,
                       '><i class="fas falink2 fa-globe"></i></a>'),
                 "")
  paste(cite, fte, icon)
}
```

<!-- ## Under review {.nohead .submitted} -->

<!-- <div class = "hangingindent"> -->

<!-- ```{r} -->
<!-- grants_submitted <- grants %>% -->
<!--   filter(type == "in-review") %>% -->
<!--   group_by(count = paste0(seq(1, nrow(.)), ".")) %>% -->
<!--   nest() %>% -->
<!--   mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>% -->
<!--   select(-data) %>% -->
<!--   unnest(cite) -->

<!-- kable(grants_submitted[1:2, ]) -->
<!-- ``` -->

<!-- </div> -->

<!-- <br class = "pageBreak"/> -->

<!-- ## Current projects {.nohead .submitted} -->

<!-- <div class = "hangingindent"> -->

<!-- ```{r} -->
<!-- grants %>% -->
<!--   filter(type == "current") %>% -->
<!--   group_by(count = paste0(seq(1, nrow(.)), ".")) %>% -->
<!--   nest() %>% -->
<!--   mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>% -->
<!--   select(-data) %>% -->
<!--   unnest(cite) %>% -->
<!--   kable() -->
<!-- ``` -->

<!-- </div> -->

<!-- <br class="pageBreak"> -->

## Completed projects {.nohead .submitted}

<div class = "hangingindent">

```{r}
grants %>%
  filter(type == "completed") %>%
  group_by(count = paste0(seq(1, nrow(.)), ".")) %>%
  nest() %>%
  mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>%
  select(-data) %>%
  unnest(cite) %>%
  kable()
```

</div>

# Teaching

<!-- <div class = "inote"> -->
<!-- Icons link to additional content   -->
</div>

## Guest-Lecturing {.nohead .tch}

```{r}
courses %>% 
  filter(type == "guest") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                         paste0( '<a href=', 
                                 website, 
                                 '><i class="fas falink fa-globe"></i></a>'),
                         ""),
         fa_git = ifelse(!is.na(repo), 
                         paste0('<a href=', 
                                repo, 
                                '><i class="fab fafooter fa-github"></i></a>'),
                         ""),
         crn = ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""),
         credits = ifelse(!is.na(credits), 
                          paste0(credits, " credit hours."),
                          ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         crn, credits,fa_git, fa_web),
         course = gsub("NA, ", "", course),
         order = paste0(order, ".")) %>% 
  select(order, course) %>% 
  kable()
```

## Teaching Assistantship {.nohead .tch}

```{r}
courses %>% 
  filter(type == "ta") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                         paste0( '<a href=', 
                                 website, 
                                 '><i class="fas falink fa-globe"></i></a>'),
                         ""),
         fa_git = ifelse(!is.na(repo), 
                         paste0('<a href=', 
                                repo, 
                                '><i class="fab fafooter fa-github"></i></a>'),
                         ""),
         fa_osf = ifelse(!is.na(repo), 
                         paste0('<a href=', 
                                repo, 
                                '><i class="fas falink2 fa-file"></i></a>'),
                         ""),
         crn = ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""),
         credits = ifelse(!is.na(credits), 
                          paste0(credits, " credit hours."),
                          ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         crn, credits,fa_web, fa_git, fa_osf),
         course = gsub("NA, ", "", course),
         order = paste0(order, ".")) %>% 
  select(order, course) %>% 
  kable()
```

# Additional Training

<div class = "nohead extratrain hangingindent">
```{r}
cv_entries %>% 
  filter(type == "extra-training") %>% 
  mutate(training = paste0(what, " (", year_end, "). ", where, "\\n")) %>% 
  select(training) %>% 
  kable()
```

</div>

<!-- <br class="pageBreak"> -->

# Professional Service

<!-- ## Working Committees {.nohead .submitted} -->

<!-- <div class = "hangingindent"> -->

<!-- ```{r} -->
<!-- committees <- cv_entries %>% -->
<!--   filter(type == "service") -->

<!-- committees %>% -->
<!--   mutate(count = paste0(seq(nrow(.), 1), "."), -->
<!--          cite = paste0(paste0("*", what, "*"), -->
<!--                        ". (",  -->
<!--                        ifelse(!is.na(year_begin),  -->
<!--                               paste0(year_begin, "-"),  -->
<!--                               ""),  -->
<!--                        year_end,  -->
<!--                        "). ", -->
<!--                        where,  -->
<!--                        ".")) %>% -->
<!--   select(count, cite) %>% -->
<!--   kable() -->
<!-- ``` -->

<!-- </div> -->

## Mentoring {.nohead .submitted}

<div class = "hangingindent">

```{r}
doc_stu <- cv_entries %>%
  filter(type == "mentoring")

doc_stu %>%
  mutate(count = paste0(seq(nrow(.), 1), "."),
         cite = paste0(what, ". (", year_begin, "-", year_end, "). ", where, ".")) %>%
  select(count, cite) %>%
  kable()

```

## Peer-Reviewing {.nohead}

<span style= 'color: #5F6A6A;'>I have served as an ad-hoc reviewer for the following journals and grants/awards:</span>

<div class = "adhoc">

```{r}
reviewer <- cv_entries %>%
  filter(type == "peer-reviewer") %>%
  select(what) %>%
  mutate(index = c(rep(1, floor(nrow(.)/2)), 
                   rep(2, nrow(.) - floor(nrow(.)/2))
                   ))


jou1 <- reviewer$what[reviewer$index == 1]
jou2 <- reviewer$what[reviewer$index == 2]

if(length(jou1) < length(jou2)) {
  jou1 <- c(jou1, NA)
}
if(length(jou2) < length(jou1)) {
  jou2 <- c(jou2, NA)
}

data.frame(jou1, jou2) %>%
  kable()
```

<br class="pageBreak">

# Awards & Honors {.history .nohead}

```{r}
cv_entries %>%
  filter(type == "award") %>%
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what,
                       "</span>"),
    what = paste0(what, ", ", where, ". ", ifelse(is.na(additional_info), "", str_c(additional_info, "."))),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
    ifelse(!is.na(additional_info),
           paste0(additional_info, "."), "")) %>%
  mutate(year = str_c(ifelse(is.na(year_begin), year_end, str_c(year_begin, " --- ", year_end)))) %>%
  select(year, what) %>%
  kable()
```

# Current Professional Affiliations {.nohead .submitted}

<div class="hangingindent prof">

```{r}
cv_entries %>%
  filter(type == "affiliation") %>%
  mutate(count = paste0(seq(nrow(.), 1), ".")) %>%
  select(what) %>%
  kable()
```

</div>